Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-08-03 xrb2/paper.tex
add some figurest p
added rotation references

We investigate the effect of rotation rate on the flame. With the exception of (citation to the weird 11 Hz flame), most observations of XRBs come from sources with rotation rates of 200-600Hz \MarginPar{check whether this is true for XRBs or just burst oscillations}. There are a number of factors that could explain this lack of observations below 200 Hz. It could be that there is some physical process which inhibits the flame ignition and/or spread at lower rotation rates. It could be that burst oscillations at lower rotation rates are smaller in amplitude and therefore more difficult to detect. It could be that it's not got anything to do with the flame at all, but that neutron stars in accreting low mass X-ray binaries rarely have rotation rates below 200 Hz \MarginPar{look into this?}.

>>>>

We investigate the effect of rotation rate on the flame. With the exception of (citation to the weird 11 Hz flame), most observations of XRBs come from sources with rotation rates of 200-600Hz \citep{bilous:2019,galloway:2020} \MarginPar{check whether this is true for XRBs or just burst oscillations}. There are a number of factors that could explain this lack of observations below 200 Hz. It could be that there is some physical process which inhibits the flame ignition and/or spread at lower rotation rates. It could be that burst oscillations at lower rotation rates are smaller in amplitude and therefore more difficult to detect. It could be that it's not got anything to do with the flame at all, but that neutron stars in accreting low mass X-ray binaries rarely have rotation rates below 200 Hz \MarginPar{look into this?}.
